\documentclass{article}
\usepackage[cm]{fullpage}
\usepackage{color}
\usepackage{hyperref}

\hypersetup{breaklinks=true,%
pagecolor=white,%
colorlinks=true,%
linkcolor=cyan,%
urlcolor=MyDarkBlue}

\definecolor{MyDarkBlue}{rgb}{0,0.0,0.45}

%%%%%%%%%%%%%%%%%%%%%%%%%%
% Formatting parameters  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newlength{\tabin}
\setlength{\tabin}{1em}
\newlength{\secsep}
\setlength{\secsep}{0.1cm}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

\definecolor{contactgray}{gray}{0.3}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Template Definitions  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-6pt} \hrulefill \\ \vspace*{-15pt}}
\newcommand{\name}[1]{\begin{center}\textsc{\Huge#1}\\\end{center}}
\newcommand{\program}[1]{\begin{center}\textsc{#1}\end{center}}
\newcommand{\contact}[1]{\begin{center}\color{contactgray}{\small#1}\end{center}}

\newenvironment{tabbedsection}[1]{
  \begin{list}{}{
      \setlength{\itemsep}{0pt}
      \setlength{\labelsep}{0pt}
      \setlength{\labelwidth}{0pt}
      \setlength{\leftmargin}{\tabin}
      \setlength{\rightmargin}{\tabin}
      \setlength{\listparindent}{0pt}
      \setlength{\parsep}{0pt}
      \setlength{\parskip}{0pt}
      \setlength{\partopsep}{0pt}
      \setlength{\topsep}{#1}
    }
  \item[]
}{\end{list}}

\newenvironment{nospacetabbing}{
    \begin{tabbing}
}{\end{tabbing}\vspace{-1.2em}}

\newenvironment{resume_header}{}{\vspace{0pt}}


\newenvironment{resume_section}[1]{
  \filbreak
  \vspace{2\secsep}
  \textsc{\large#1}
  \lineunder
  \begin{tabbedsection}{\secsep}
}{\end{tabbedsection}}

\newenvironment{resume_subsection}[2][]{
  \textbf{#2} \hfill {\footnotesize #1} \hspace{2em}
  \begin{tabbedsection}{0.5\secsep}
}{\end{tabbedsection}}

\newenvironment{subitems}{
  \renewcommand{\labelitemi}{-}
  \begin{itemize}
      \setlength{\labelsep}{1em}
}{\end{itemize}}

\newenvironment{resume_employer}[4]{
  \vspace{\secsep}
  \textbf{#1} \\ 
  \indent {\small #2} \hfill {\footnotesize#3 (#4)}
  \begin{tabbedsection}{0pt}
  \begin{subitems}
}{\end{subitems}\end{tabbedsection}}


%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Start Document     %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{resume_header}
	\name{Otavio Sartorelli de Toledo Piza}
	\program{Computer Science Honors}
	\contact{otaviostpiza@gmail.com \hspace{1cm} \href{https://github.com/OtavioPiza}{github.com/OtavioPiza} \hspace{1cm} +1 765 637 6927	 \hspace{1cm}Student ID: 0032690213}
\end{resume_header}

\begin{resume_section}{About Me}
  
  \begin{nospacetabbing}
  	\textbf{Technical Skills}  \= C/C++, Python, Jupyter Notebooks, TypeScript, JavaScript, Java,  Bash, SQL, Dart, \LaTeX, R. \\*
  	\textbf{Technologies} \> Express, React, Angular, Git, CMAKE, MongoDB, PostgreSQL, Firebase, Docker. \\*
  	\textbf{Languages} \> English (C2), German (B2), Spanish (B2), Portuguese (native). \\*
  	\textbf{Interests} \> Analysis of Algorithms, Databases, Search, Systems Programming, Security.\\*
  \end{nospacetabbing}

\end{resume_section}

\begin{resume_section}{Work Experience}

	\begin{resume_subsection}[Irvine, CA (2022.05 -- 2022.08)]{Google -- STEP Intern}
		\begin{subitems}
			\item Created a \textbf{full-stack web application} for \textbf{searching inside an internal tool} for a user-specified resource, \textbf{improving system stability} by removing the need to perform error-prone manual searches and \textbf{facilitating debugging}.
			\item Developed an \textbf{SQL database query} to search for a user-specified resource inside an internal tool's storage.
			\item Built a back-end \textbf{RPC service with C++} responsible for processing query requests received through a \textbf{Java proxy} service from the front-end and responding with the appropriate resources.
			\item Implemented a \textbf{generic filter model} for front-end tables, \textbf{facilitating adding data filtration} functionality and \textbf{reducing boilerplate code} between different components.
			\item Developed a front-end page utilizing \textbf{AngularDart}, allowing users to query for resources from a back-end service and see the results in a table.
		\end{subitems}	
	\end{resume_subsection}
	
	\begin{resume_subsection}[Remote (2021.08 -- present)]{BRASA -- Fullstack Developer}
		\begin{subitems}
			\item Created a \textbf{unified authentication system}, which supports \textbf{multiple user types and access levels}.
			\item Established an \textbf{internal tool request and development process}, \textbf{reducing delivery time by 300\%}.
			\item Refactored our API into a \textbf{centralized domain-driven design}, improving \textbf{maintainability and expandability}.
			\item Developed a full-stack LinkTree-like app to \textbf{allow users to easily share their profiles} during a conference. 
		\end{subitems}
	\end{resume_subsection}

\end{resume_section}


\begin{resume_section}{Personal Projects}

	\begin{resume_subsection}[\href{https://www.github.com/OtavioPiza/restpp}{github.com/OtavioPiza/restpp}]{REST++ -- C++ REST Framework}
		\begin{subitems}
			\item Developed web sockets using the \textbf{C socket library}, allowing clients to connect to the server.
			\item Implemented \textbf{multiple execution modes, both concurrent and single-threaded}, enabling the user to \textbf{choose the one better suited to their needs}.
			\item Designed a \textbf{graph-based routing system} dispatching the \textbf{requests to the appropriate handlers}.
			\item Working on \textbf{building a request-body parser}.
		\end{subitems}
	\end{resume_subsection}
	
	\begin{resume_subsection}[\href{https://www.github.com/OtavioPiza/restpp}{github.com/OtavioPiza/restpp}]{TodoDoro -- Productivity TODO List}
 		\begin{subitems}
 			\item Developed a full-stack web-based application with \textbf{MongoDB, Express, React, and NodeJS}, allowing users to \textbf{create tasks and work on them according to the Pomodoro method}.
 			\item Implemented a \textbf{JSONWebToken-based authentication system}.
 			\item Working on \textbf{sending verification emails after account creation}.
 		\end{subitems}
	\end{resume_subsection}

\end{resume_section}

\begin{resume_section}{Education}
  
  \begin{resume_subsection}[West Lafayette, IN (2020.08 -- 2024.05)]{Purdue University}
    
    \begin{subitems}
      \item Bachelor of Computer Science Honors.
      \item Grade Point Average: 3.96 / 4.00.  	
  	  \item Dean's List \& Semester Honors: Fall 2020, Spring 2021, Fall 2021, Spring 2022.
  	  \item Relevant Coursework: \textbf{Analysis Of Algorithms} (Planned Spring 2023), \textbf{Intro to Relational Databases} (Planned Spring 2023), \textbf{Software Testing} (Planned Spring 2023), \textbf{Web Info Search \& Management} (Fall 2022), \textbf{Operating Systems} (Fall 2022), \textbf{Information Systems} (Fall 2022), \textbf{Software Engineering I} (Spring 2022), \textbf{Systems Programming} (Spring 2022), \textbf{Data Structures and Algorithms} (Fall 2021).
  	  \item Teaching Assistant: Competitive Programming I (Fall 2022).
	\end{subitems}  	
  	
  \end{resume_subsection}
  
\end{resume_section}

\begin{resume_section}{Student Organizations}

	\begin{resume_subsection}{LauchPad -- Treasurer}
    \begin{subitems}
		\item Responsible for \textbf{managing the club's funds} for events.
		\item Helped \textbf{plan mentorship program} where \textbf{first-year mentees get help from upperclassmen mentors} developing their projects.
		\item Helped \textbf{organize an event with AT\&T} where \textbf{club mentees we able to present their projects} to recruiters and engineers their projects.
		\item Working on \textbf{developing a website club}.
	\end{subitems}  
	\end{resume_subsection}
	
	
\end{resume_section}

\end{document}