\documentclass[]{article}
\usepackage[cm]{fullpage}
\usepackage{color}
\usepackage{hyperref}
\usepackage[margin=0.5in]{geometry}

\hypersetup{
	breaklinks=true,
	pagecolor=white,
	colorlinks=true,
	linkcolor=cyan,
	urlcolor=_darkblue,
}

\definecolor{_darkblue}{rgb}{0,0.0,0.45}

%%%%%%%%%%%%%%%%%%%%%%%%%%
% Formatting parameters  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newlength{\tabin}
\setlength{\tabin}{1em}
\newlength{\secsep}
\setlength{\secsep}{0.1cm}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

\definecolor{contactgray}{gray}{0.3}
\pagestyle{empty}

%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Template Definitions  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-6pt} \hrulefill \\ \vspace*{-15pt}}
\newcommand{\name}[1]{\begin{center}\textsc{\Huge#1}\\\end{center}}
\newcommand{\program}[1]{\begin{center}\textsc{#1}\end{center}}
\newcommand{\contact}[1]{\begin{center}\color{contactgray}{\small#1}\end{center}}

\newenvironment{tabbedsection}[1]{
  \begin{list}{}{
      \setlength{\itemsep}{0pt}
      \setlength{\labelsep}{0pt}
      \setlength{\labelwidth}{0pt}
      \setlength{\leftmargin}{\tabin}
      \setlength{\rightmargin}{\tabin}
      \setlength{\listparindent}{0pt}
      \setlength{\parsep}{0pt}
      \setlength{\parskip}{0pt}
      \setlength{\partopsep}{0pt}
      \setlength{\topsep}{#1}
    }
  \item[]
}{\end{list}}

\newenvironment{nospacetabbing}{
    \begin{tabbing}
}{\end{tabbing}\vspace{-1.2em}}

\newenvironment{resume_header}{}{\vspace{0pt}}


\newenvironment{resume_section}[1]{
  \filbreak
  \vspace{2\secsep}
  \textsc{\large#1}
  \lineunder
  \begin{tabbedsection}{\secsep}
}{\end{tabbedsection}}

\newenvironment{resume_subsection}[2][]{
  \textbf{#2} \hfill {\footnotesize #1} \hspace{2em}
  \begin{tabbedsection}{0.5\secsep}
}{\end{tabbedsection}}

\newenvironment{subitems}{
  \renewcommand{\labelitemi}{-}
  \begin{itemize}
      \setlength{\labelsep}{1em}
}{\end{itemize}}

\newenvironment{resume_employer}[4]{
  \vspace{\secsep}
  \textbf{#1} \\
  \indent {\small #2} \hfill {\footnotesize#3 (#4)}
  \begin{tabbedsection}{0pt}
  \begin{subitems}
}{\end{subitems}\end{tabbedsection}}


%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Start Document     %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{resume_header}

	\name{Otavio Sartorelli de Toledo Piza}

	\program{Computer Science Honors}

	\contact{otaviostpiza@gmail.com
		\hspace{1cm}
		\href{https://github.com/OtavioPiza}{github.com/OtavioPiza}
		\hspace{1cm} +1 765 637 6927
		\hspace{1cm}Student ID: 0032690213}

\end{resume_header}

\begin{resume_section}{About Me}

	\begin{nospacetabbing}

		\textbf{Technical Skills}  \= C/C++, Python, Jupyter Notebooks, TypeScript, JavaScript,
		Java,  Bash, SQL, Dart, \LaTeX, R. \\*

		\textbf{Technologies} \> Express, React, Angular, Git, CMAKE, MongoDB, PostgreSQL,
		Firebase, Docker. \\*

		\textbf{Languages} \> English (C2), German (B2), Spanish (B2), Portuguese (native). \\*

		\textbf{Interests} \> Analysis of Algorithms, Databases, Search,
		Security, Distributed Systems, Infrastructure.\\*

	\end{nospacetabbing}

\end{resume_section}

%%%%%%%%%%%%%%%%%%%%%%%%%
%    Work Experience    %
%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resume_section}{Work Experience}

	\begin{resume_subsection}[Boulder, CO (2023.05 -- Current)]{Google -- Software Engineering Intern}

		\begin{subitems}

			\item Developing an end-to-end debugging framework for Google Search's notification
			infrastructure responsible for serving over 2 billion users. The new framework enables
			partner teams to safely manipulate the live system even in a production environment
			without affecting non-targeted users or introducing breaking changes, thus significantly
			facilitating debugging new and existing features. Additionally, the new tool
			guarantees developers' changes are enforced for their time to live, after which
			they automatically are reversed.

			% \subitem Extending an internal web application to support the new features which will
			% enable users more easily interact with the framework through a GUI.

		\end{subitems}

	\end{resume_subsection}

	\begin{resume_subsection}[Irvine, CA (2022.05 -- 2022.08)]{Google -- STEP Intern}

		\begin{subitems}

			\item Created a full-stack web application for searching for a user-specified resoucrce
			in an internal tool, improving system stability by removing the need to perform
			error-prone manual searches and facilitating debugging.

			\item Developed an SQL database query to search for a user-specified resource inside
			an internal tool's storage.

			\item Built a back-end RPC service with C++ responsible for processing query requests
			received through a Java proxy service from the front-end and responding with the
			appropriate resources.

			\item Implemented a generic filter model for front-end tables, facilitating adding
			data filtration functionality and reducing boilerplate code between different components.

			\item Developed a front-end page utilizing AngularDart, allowing users to query for
			resources from a back-end service and see the results in a table.

		\end{subitems}

	\end{resume_subsection}

\end{resume_section}

%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    Personal Projects    %
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resume_section}{Projects}

	\begin{resume_subsection}[
			\href{https://www.github.com/OtavioPiza/servercc}{github.com/OtavioPiza/restpp}
		]{SERVERCC -- Distributed IOT Framework}

		\begin{subitems}

			\item Developing a completely decentralized framework for IOT using the C socket library.

			\item Implemented an auto initialization sequence in which a node utilizes one-to-many
			network communications to learn about other nodes and their services, 
			allowing for dynamic asymmetric servers.

			\item Designed a message demultiplexing system that enables multiple threads of
			execution per node.

			\item Implemented a recovery system that gracefully handles other nodes disconnecting
			unexpectedly.

			\item Working on implementing a routing protocol that supports arbitrary indirect
			connections between nodes.

		\end{subitems}

	\end{resume_subsection}

	\begin{resume_subsection}[
		\href{https://github.com/real-xinu}{github.com/real-xinu}
	]{Xinu Lab}

		\begin{subitems}

			\item Fixed a resource deallocation issue in the operating system's shell which could
			lead to crashes. This unblocked a major update that introduced pipes to the shell.

			\item Working on implementing support for concurrent file access among many processes.

		\end{subitems}

	\end{resume_subsection}

\end{resume_section}

%%%%%%%%%%%%%%%%%%%
%    Education    %
%%%%%%%%%%%%%%%%%%%

\begin{resume_section}{Education}

	\begin{resume_subsection}[West Lafayette, IN (2020.08 -- 2024.05)]{Purdue University}

		\begin{subitems}

			\item Bachelor of Computer Science Honors.
			
			\item Dean's List and Semester Honors (Fall 2020 -- Spring 2023)

			\item Grade Point Average: 3.96 / 4.00.

			\item Teaching Assistant: Competitive Programming I \& II (Fall 2022 -- Current).
			Created solutions for homework problems. Hosted biweekly office hours to answer
			student questions. Lead problem discussions after class.

		\end{subitems}

	\end{resume_subsection}

\end{resume_section}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    Student Organizations    %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{resume_section}{Student Organizations}

	\begin{resume_subsection}[Remote (2021.08 -- 2022.08)]{BRASA -- Fullstack Developer}

		\begin{subitems}

			\item Created a unified authentication system, which supports multiple user types and
			access levels.

			\item Established an internal tool request and development process, reducing delivery
			time by 300\%.

			\item Refactored our API into a centralized domain-driven design, improving
			maintainability and expandability.

			\item Onboarded new developers into the organization's systems.

		\end{subitems}

	\end{resume_subsection}

\end{resume_section}

\end{document}
